--- 
title: "General Education Course Registrations^[Report number 1702, DOI [10.17605/OSF.IO/MRJBD](https://doi.org/10.17605/OSF.IO/MRJBD)]"
subtitle: "An Overview of Registration Patterns for Fall 2017"
author: 
  - "Dr. Clifton Franklund"
  - "General Education Coordinator"
date: "Fall 2017"
output: 
  bookdown::gitbook:
    includes:
      after_body: disqus.html
description: An analysis of course registration patterns for fall 2017. This report may be used to evaluate the overall participation of units in assessment and the distribution of assessment methods.
documentclass: article
github-repo: WeeBeasties/1702
link-citations: yes
bibliography: references.bib
site: bookdown::bookdown_site
biblio-style: apalike
---
\addtolength{\headheight}{0.7cm}
\thispagestyle{fancyplain}
\lhead{\includegraphics[height=0.5cm]{art/logo.png}}
\rhead{}
\renewcommand{\headrulewidth}{0pt}

```{R packages, echo=FALSE, message=FALSE, warning=FALSE}

#----------------------------------------------------------------------------------------
#	LOAD PACKAGES
#----------------------------------------------------------------------------------------

library(tidyverse)	# tidy data science
library(googlesheets)   # scrape Google sheet data from the web
library(pander)         # used to report session settings
```


# Abstract {#abstract -}
> _Assessment is not a spreadsheet; it's a conversation._
> --- Irmeli Halinen

In an effort to get uniform and systematic assessment data, all faculty teaching courses with General Education attributes were asked to voluntarily register. These registrations were facilitated using a Google form and the data were gathered in a Google sheet. This document summarizes the results of those activities for the fall semester of 2017. Here are links to different versions of this report:  

* [Multi-part HTML](http://reproducibleassessment.com/1702)  
* [Single-page HTML](http://reproducibleassessment.com/1702/Report-1702.html)  
* [PDF](http://reproducibleassessment.com/1702/Report-1702.pdf)  

# Introduction {#introduction -}
This is the first semester of assessing our revised General Education program at Ferris State University. To simplify and automate data reporting, TracDat assignments will be sent to all General Education instructors. Each faculty member will assess FLO3 this semester. Each can select any of the 14 pre-defined measures to evaluate their student's work. With 10 competencies (2 diversity and 2 communication), each with 14 measures, there are 140 different possibilities for assignments. To keep all of this straight, a registration process has been created. This report summarizes the course registrations that were made in fall 2017.

# Methods {#methods -}

## Data provenance {-}
Data provenance refers to a system that permits tracking of the origin, movement, modification, and utilization of data sets [@Buneman2001]. The provenance of General Education data will be explicitly declared to facilitate the reproducibility and extensibility of these studies.

### Location of public website files {-}
All files related to this report can be found online at the Open Science Framework [@Nosek2012]. This site contains all of the files needed to reproduce this report from the de-identified data set. The site's url is [https://osf.io/t6u8m/](https://osf.io/mrjbd/).

### Session information {-}
This report was written using RStudio [@Rstudio] and the R statistical programming language [@R]. These products are free to download for PC, Macintosh, and Linux operating systems. The following information pertains to the session parameters used to generate this report. If you have trouble reproducing this report, it may be due to different session parameters. You may contact [Dr. Franklund](mailto:CliftonFranklund@ferris.edu) if you need assistance.

```{R Session, echo=FALSE, comment=FALSE, error=FALSE, results='asis'}
pander(sessionInfo())
```

### Processing instructions {-}
This project produced a computationally reproducible assessment report (this document). Anyone wishing to recreate this report from the source document will need to install the following on their computer:

1. [An installation of the R programming language](https://www.r-project.org)
2. [An installation of the RStudio IDE](https://www.rstudio.com/products/rstudio/download3/)
3. [An installation of LaTeX](https://www.latex-project.org/get/)

The necessary source files include the de-identified data set (BIOL200Data.csv), Rmarkdown code files (index.Rmd, 01-Introduction.Rmd, 02-Methods.Rmd, 03-Results.Rmd, 04-Discussion.Rmd, and 05-References.Rmd), bibtex reference file (references.bib), and custom art file in the /art folder.

To process the files, you must first open the project in RStudio. Click on the "Build Book" button in the Build menu. Bookdown allows you to build this project as git_book (html site), pdf_book (via LaTeX), or epub_book (compatible with iBooks and other e-book readers).

### Citation of this work {-}
All of the de-identified data, analysis code, and documentation that constitute this report project may be freely used, modified, and shared. The de-identified data set, BIOL200Data.csv, is released under the Creative Commons [CC0 license](https://creativecommons.org/publicdomain/zero/1.0/). All documentation, including README.md, Codebook.md, and this report, are released under the Creative Commons [CC-BY](https://creativecommons.org/licenses/by/4.0/) licence. Any questions, comments, or suggestions may be sent to [Dr. Franklund](mailto:CliftonFranklund@ferris.edu).

## Retrieving the registration data {#googlesheets -}  
```{R getData, echo=FALSE, message=FALSE, warning=FALSE}
#####################################################################
# UNCOMMENT THIS BLOCK TO GET THE DATA FROM GOOGLE
# authentication may be required via a web browswer for access...
#####################################################################
#myGoogleSheet <- gs_title("Core Competency Assessment  (Responses)")
#rawData <- myData <- gs_read(ss = myGoogleSheet, ws = "Form Responses 1")
#names(rawData)[names(rawData) == 'CORE COMPETENCY'] <- 'COMPETENCY'
#names(rawData)[names(rawData) == 'STANDARD MEASURE'] <- 'MEASURE'
#
#myDups <- rawData %>% group_by(COMPETENCY,EMAIL,MEASURE) %>% filter(n()>1) %>% arrange(EMAIL,MEASURE,COMPETENCY,COURSE)
#
#myData <- as.data.frame(rawData)
#myData$COMPETENCY <- as.factor(myData$COMPETENCY)
#myData$COMPETENCY <- factor(myData$COMPETENCY, levels=rev(levels(myData$COMPETENCY)))
#
#myData$MEASURE <- as.factor(myData$MEASURE)
#myData$MEASURE <- factor(myData$MEASURE, levels=rev(levels(myData$MEASURE)))
#myData <- myData[ ,-c(1,4,5,7,8)]
#
#write.csv(myData, file="data/registrations.csv", row.names = FALSE)
#write.csv(myData, file="docs/data/registrations.csv", row.names = FALSE)

#####################################################################
# UNCOMMENT THIS BLOCK TO READ THE CSV FILE FOR THE DATA
# personal identifying information has been removed...
#####################################################################
myData <- read.csv("data/Fall2017.csv")
names(myData)[names(myData) == 'CORE.COMPETENCY'] <- 'COMPETENCY'
names(myData)[names(myData) == 'STANDARD.MEASURE'] <- 'MEASURE'
myData$COMPETENCY <- factor(myData$COMPETENCY, levels = rev(levels(myData$COMPETENCY))) 
myData$MEASURE <- factor(myData$MEASURE, levels = rev(levels(myData$MEASURE)))

```

## Data collection {#data -}
All registration records for the fall of 2017 were collated and de-identified. The data file, 'registrations.csv', contains only the course name (e.g. BIOL 101), the core competency (e.g. Natural Sciences), and the standardized measure (e.g. Selected Response Exam). The datafile is [available here](data/registrations.csv).

# Results and Discussion {#results -}  
```{R summarizeData, echo=FALSE, message=FALSE, warning=FALSE}
competencyCounts <- myData %>%
	group_by(COMPETENCY) %>%
	summarise(COUNT=n())

measureCounts <- myData %>%
	group_by(MEASURE) %>%
	summarise(COUNT=n())
```
 
A total of `r length(myData$COMPETENCY)` registrations were submitted for the Fall 2017 semester. This represented the efforts of `r length(unique(myData$NAME))` different faculty members and included a total of `r length(unique(myData$COURSE))` different courses. The distribution of the registrations between the eight core competencies is shown in figure \@ref(fig:competency). As can be seen, at least 16 registrations were made for each of the competencies. Culture and Diversity had the most registrations, while Collaboration and Problem Solving had the fewest.

```{r competency, echo=FALSE, fig.cap="Distribution of course registrations by core competency."}
# Plot of registrations by competency -------------------------------------
ggplot(competencyCounts, aes(x=COMPETENCY, y=COUNT)) +
	geom_bar(stat = "identity", fill = "Firebrick") +
	geom_text(aes(label = COUNT, y = COUNT + 2.0),position = position_dodge(0), vjust = 0.5) +
	theme_classic(base_size = 14) +
	coord_flip()
```

```{block, type='question'}
Do you think that this represents a sufficient number of registrations for the semester? How can we improve the participation in Collaboration and Problem Solving?
```

The registrations were further broken down by the types of measures being employed by the faculty. Using our fourteen standard measures...

- A total of `r sum(measureCounts[11:14, 2])` exams were registered (`r round(sum(measureCounts[11:14, 2])/length(myData$COMPETENCY)*100,1)`%).  
- A total of `r sum(measureCounts[4:10, 2])` student products were registered (`r round(sum(measureCounts[4:10, 2])/length(myData$COMPETENCY)*100,1)`%).  
- A total of `r sum(measureCounts[1:3, 2])` student performances were registered (`r round(sum(measureCounts[1:3, 2])/length(myData$COMPETENCY)*100,1)`%).  

```{r measure, echo=FALSE, fig.cap="Distribution of course registrations by standardized measure."}
# Plot of registrations by measure ----------------------------------------
ggplot(measureCounts, aes(x=MEASURE, y=COUNT)) +
	geom_bar(stat = "identity", fill = "Firebrick") +
	geom_text(aes(label = COUNT, y = COUNT + 3.0),position = position_dodge(0), vjust = 0.5) +
	theme_classic(base_size = 12) +
	coord_flip()
```

```{block, type='question'}
Do you think that there are too many exams in this mix? What is the desired balance between exams, products, and performances for General Education?
```

Now that our first round of registrations has been completed, I would appreciate some feedback.

```{block, type='question'}
Was this overly difficult or confusing?   
How can the process be improved for future semesters?
```


